Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-05-29 Manuscript/TEM_draft.tex
Results tables

\begin{table}[ht]
\caption{Statistical tests}
\centering
\begin{tabular}{lrll}
  \hline
   & test & statistics & code\{package\} \\ [0.5ex]
  \hline
  Groups comparisons & ANOVA & parametric & anova\{stats\} \\ [0.5ex]
                     & Kruskal-Wallis & non-parametric & kruskal.test\{stats\} \\[0.5ex]
  \hline
  Pairwise comparisons & Tukey HSD & parametric & TukeyHSD\{stats\} \\ [0.5ex]
                       & Nemenyi-Damico-Wolfe-Dunn & non-parametric & kruskalmc\{pgirmess\} \\ [0.5ex]
  \hline
\end{tabular}
\end{table}
\label{Stats_test}

@@

%Tables model...

% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Wed May 28 17:54:17 2014
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & Kruskal.Wallis.chi.squared & df & p.value \\ 
  \hline
1 & 65.62 & 4.00 & 0.00 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.0.2 by xtable 1.7-1 package
% Wed May 28 17:54:17 2014
\begin{table}[ht]
\centering
\begin{tabular}{rrrl}
  \hline
 & obs.dif & critical.dif & difference \\ 
  \hline
1-2 & 45.87 & 41.00 & TRUE \\ 
  1-3 & 60.33 & 41.00 & TRUE \\ 
  1-4 & 76.83 & 41.00 & TRUE \\ 
  1-5 & 99.80 & 41.00 & TRUE \\ 
  2-3 & 14.46 & 41.00 & FALSE \\ 
  2-4 & 30.96 & 41.00 & FALSE \\ 
  2-5 & 53.93 & 41.00 & TRUE \\ 
  3-4 & 16.50 & 41.00 & FALSE \\ 
  3-5 & 39.47 & 41.00 & FALSE \\ 
  4-5 & 22.97 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\caption{Statistical tests}
\centering
\begin{tabular}{lrll}
  \hline
   & test & statistics & code\{package\} \\ [0.5ex]
  \hline
  Groups comparisons & ANOVA & parametric & anova\{stats\} \\ [0.5ex]
                     & Kruskal-Wallis & non-parametric & kruskal.test\{stats\} \\[0.5ex]
  \hline
  Pairwise comparisons & Tukey HSD & parametric & TukeyHSD\{stats\} \\ [0.5ex]
                       & Nemenyi-Damico-Wolfe-Dunn & non-parametric & kruskalmc\{pgirmess\} \\ [0.5ex]
  \hline
\end{tabular}
\label{Stats_test}
\end{table}

@@

%Tables model...
\begin{table}
\caption{Group difference per configuration set}
\centering
\begin{tabular}{rlrllll}
    \hline
    set & metric & framework & parametric & $stats^1$ & df & p.value \\
    \hline
    $M_L$ & Robinson-Fould & ML & bla & bla & bla & bla \\
          &                & Bayesian & no & 65.62 & 4.00 & \textbf{0.00} \\
          & Triples & ML & bla & bla & bla & bla \\
          &         & Bayesian & no & 4.56 & 4.00 & 0.34 \\
    $M_F$ & Robinson-Fould & ML & bla & bla & bla & bla \\
          &                & Bayesian & no & 85.61 & 4.00 & \textbf{0.00} \\
          & Triples & ML & bla & bla & bla & bla \\
          &         & Bayesian & no & 3.01 & 4.00 & 0.56 \\ 
    $M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
          &                & Bayesian & no & 64.23 & 4.00 & \textbf{0.00} \\
          & Triples & ML & bla & bla & bla & bla \\
          &         & Bayesian & no & 26.13 & 24.00 & 0.35 \\
    $M_L+M_F$ & Robinson-Fould & ML & bla & bla & bla & bla \\
              &                & Bayesian & no & 317.97 & 24.00 & \textbf{0.00} \\
              & Triples & ML & bla & bla & bla & bla \\
              &         & Bayesian & no & 3.01 & 4.00 & 0.56 \\ 
    $M_L+M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
              &                & Bayesian & no & 290.10 & 24.00 & \textbf{0.00} \\
              & Triples & ML & bla & bla & bla & bla \\
              &         & Bayesian & no & 22.19 & 24.00 & 0.57 \\ 
    $M_F+M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
              &                & Bayesian & no & 385.96 & 24.00 & \textbf{0.00} \\
              & Triples & ML & bla & bla & bla & bla \\
              &         & Bayesian & no & 20.23 & 24.00 & 0.68 \\
    $M_L+M_F+M_C$ & Robinson-Fould & ML & bla & bla & bla & bla \\
                  &                & Bayesian & no & 1167.40 & 124.00 & \textbf{0.00} \\
                  & Triples & ML & bla & bla & bla & bla \\
                  &         & Bayesian & no & 115.86 & 124.00 & 0.69 \\ 
    \hline
\label{Group_results}
\end{tabular}

$^1$ F-value for parametric tests and Kruskal Wallis $chi^2$ for non parametric tests.
\end{table}

\begin{table}
\caption{$M_L$ non-parametric pairwise difference for Robinson-Fould metric}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_L$00\% & $M_L$10\% & $M_L$25\% & $M_L$50\% & $M_L$75\% \\
    \hline
    $M_L$00\% & - & FALSE & \textbf{TRUE} & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_L$50\% & & & & - & FALSE \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_L$00\%-$M_L$10\% & 17.05 & 41.00 & FALSE \\ 
  $M_L$00\%-$M_L$25\% & 43.79 & 41.00 & TRUE \\ 
  $M_L$00\%-$M_L$50\% & 77.32 & 41.00 & TRUE \\ 
  $M_L$00\%-$M_L$75\% & 103.99 & 41.00 & TRUE \\ 
  $M_L$10\%-$M_L$25\% & 26.75 & 41.00 & FALSE \\ 
  $M_L$10\%-$M_L$50\% & 60.27 & 41.00 & TRUE \\ 
  $M_L$10\%-$M_L$75\% & 86.94 & 41.00 & TRUE \\ 
  $M_L$25\%-$M_L$50\% & 33.53 & 41.00 & FALSE \\ 
  $M_L$25\%-$M_L$75\% & 60.20 & 41.00 & TRUE \\ 
  $M_L$50\%-$M_L$75\% & 26.67 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{ML_results}
\end{table}

\begin{table}
\caption{$M_F$ non-parametric pairwise difference for Robinson-Fould metric in Bayesian framework}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_F$00\% & $M_F$10\% & $M_F$25\% & $M_F$50\% & $M_F$75\% \\
    \hline
    $M_L$00\% & - & FALSE & FALSE & \textbf{TRUE} & \textbf{TRUE}\\
    $M_L$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_L$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_L$50\% & & & & - & FALSE \\
    $M_L$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_F$00\%-$M_F$10\% & 16.03 & 41.00 & FALSE \\ 
  $M_F$00\%-$M_F$25\% & 38.50 & 41.00 & FALSE \\ 
  $M_F$00\%-$M_F$50\% & 61.52 & 41.00 & TRUE \\ 
  $M_F$00\%-$M_F$75\% & 95.52 & 41.00 & TRUE \\ 
  $M_F$10\%-$M_F$25\% & 22.47 & 41.00 & FALSE \\ 
  $M_F$10\%-$M_F$50\% & 45.49 & 41.00 & TRUE \\ 
  $M_F$10\%-$M_F$75\% & 79.49 & 41.00 & TRUE \\ 
  $M_F$25\%-$M_F$50\% & 23.02 & 41.00 & FALSE \\ 
  $M_F$25\%-$M_F$75\% & 57.02 & 41.00 & TRUE \\ 
  $M_F$50\%-$M_F$75\% & 34.00 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{MF_results}
\end{table}

\begin{table}
\caption{$M_C$ non-parametric pairwise difference for Robinson-Fould metric in Bayesian framework}
\centering
\begin{tabular}{c|ccccc}
    \hline
              & $M_C$00\% & $M_C$10\% & $M_C$25\% & $M_C$50\% & $M_C$75\% \\
    \hline
    $M_C$00\% & - & FALSE & FALSE & \textbf{TRUE} & \textbf{TRUE}\\
    $M_C$10\% & & - & FALSE & \textbf{TRUE} & \textbf{TRUE} \\
    $M_C$25\% & & & - & FALSE & \textbf{TRUE} \\
    $M_C$50\% & & & & - & FALSE \\
    $M_C$75\% & & & & & - \\
    \hline
\end{tabular}
\centering
\begin{tabular}{rrrl}
 pairwise comparison & obs.dif & critical.dif & difference \\ 
  \hline
  $M_C$00\%-$M_C$10\% & 16.03 & 41.00 & FALSE \\ 
  $M_C$00\%-$M_C$25\% & 38.50 & 41.00 & FALSE \\ 
  $M_C$00\%-$M_C$50\% & 61.52 & 41.00 & TRUE \\ 
  $M_C$00\%-$M_C$75\% & 95.52 & 41.00 & TRUE \\ 
  $M_C$10\%-$M_C$25\% & 22.47 & 41.00 & FALSE \\ 
  $M_C$10\%-$M_C$50\% & 45.49 & 41.00 & TRUE \\ 
  $M_C$10\%-$M_C$75\% & 79.49 & 41.00 & TRUE \\ 
  $M_C$25\%-$M_C$50\% & 23.02 & 41.00 & FALSE \\ 
  $M_C$25\%-$M_C$75\% & 57.02 & 41.00 & TRUE \\ 
  $M_C$50\%-$M_C$75\% & 34.00 & 41.00 & FALSE \\ 
   \hline
\end{tabular}
\label{MC_results}
\end{table}
